\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading{Graduate Research Assistant}{%
  Aug 2025 -- Present\vspace{-2pt}%
}{%
  \href{https://gatech.edu}{Georgia Institute of Technology}%
}{Atlanta, GA}

\vspace{4pt}
\small%
Working as a graduate research assistant in the \underline{\href{https://kamoamoa.com/}{Ka Moamoa Lab}}.
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Working on timekeeping for low-power embedded and edge devices.}

\resumeItemListEnd

\normalsize


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeSubheading{Machine Learning Developer}{%
  Sep 2024 -- Present\vspace{-2pt}%
}{%
  \href{https://cat.com}{Caterpillar, Inc.}%
}{Remote (consulting)}

\vspace{4pt}
\small%
Worked part-time in the Autonomy and Automation Division on Machine Learning pipelines.%
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Helped bring the project to an MVP and create an initial deployment.}

\resumeItem{Worked with architect on major design decisions.}

\resumeItem{Responsible for the design and implementation of key features.}

\resumeItem{Continuation of work from internship.}

\resumeItemListEnd

\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeSubheading{Undergraduate Researcher}{%
  Sep 2022 -- Jun 2025\vspace{-2pt}%
}{%
  \href{https://paragon.cs.northwestern.edu/\#Research}{PARAG@N Lab}%
}{Evanston, IL}


\vspace{4pt}
\small{Led a research project to design improved Quantum Systems software.}%\normalsize
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Designed and programmed a quantum compiler to optimize quantum circuits for emerging quantum computer topologies.}

\resumeItem{Created a development framework and tools for further quantum systems research.}

\resumeItem{Student leader of the project while an undergraduate student.}

\resumeItemListEnd

\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeSubheading{Software Engineering Intern}{%
  Jun 2024 -- Aug 2024\vspace{-2pt}%
}{%
  \href{https://cat.com}{Caterpillar, Inc.}%
}{Peoria, IL}


\vspace{4pt}
\small{Worked in the Autonomy and Automation Division on computer vision and
  data processing.}
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Worked on the design and implementation of a new data warehouse
  and processing pipeline in Python.}

\resumeItem{Designed and implemented distributed concurrency control systems
  for distributed compute with ZooKeeper.}

\resumeItem{Worked a smartphone vehicle calibration system using OpenCV in
  Python.}

\resumeItem{Learned about commercial robotics and autonomy platforms.}

\resumeItemListEnd

\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeSubheading{Teaching Assistant}{%
  Jun 2023 -- Jun 2024\vspace{-2pt}%
}{%
  \href{https://www.mccormick.northwestern.edu/computer-science/academics/undergraduate/peer-mentor-program/}{Northwestern University}%
}{Evanston, IL}


\vspace{4pt}
\small{Acted as an undergraduate peer mentor for CS 321: Programming Languages
  and CS 213: Intro to Computer Systems.}%\normalsize
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Held several office hours each week.}

\resumeItem{Answered questions, both synchronously in office hours and asynchronously on a Piazza message board.}

\resumeItemListEnd

\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resumeSubheading{Campus Ambassador}{%
  Sep 2023 -- Jun 2024\vspace{-2pt}%
}{%
  \href{https://ansys.com}{Ansys, Inc.}%
}{Evanston, IL}

\vspace{4pt}
\small{Acted as the Campus Ambassador for Ansys at Northwestern.}
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Researched, reached out to, and scheduled meetings with relevant campus groups to discuss Ansys' tools.}

\resumeItem{Organized lunch info sessions for Ansys, including booking rooms and organizing food.}

\resumeItem{Coordinated with a member of the Ansys team for the campus work.}

\resumeItemListEnd

\normalsize



\resumeSubHeadingListEnd
