\section{Experience}

\resumeSubHeadingListStart



\resumeSubheading{Software Engineer}{%
  Jun 2023 -- Present\vspace{-2pt}%
}{%
  \href{https://www.nikola.cx/projects/nuft}{Northwestern Fintech Club}%
}{Evanston, IL}


\vspace{4pt}
\small{Help build and maintain a trading infrastructure using C++, Python, CMake, Machine Learning, libcurl, and libuv.}%\normalsize
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Created a orderbook system to pull orderbooks from exchanges using libcurl and libuv, then push them into a Redis instance for consumption by ML prediction clients.}

\resumeItem{Organized linting and build systems for multiple projects, in C++ and Python.}

\resumeItem{Helped create a devlopment architecture for the coming years, with a focus on reducing technical debt.}

\resumeItemListEnd

\normalsize
\vspace{-4pt}


\resumeSubheading{Summer Undergraduate Researcher}{%
  Jun 2023 -- Sep 2023\vspace{-2pt}%
}{%
  \href{http://paragon.cs.northwestern.edu/\#Research}{PARAG@N Lab}%
}{Evanston, IL}


\vspace{4pt}
\small{Funded by an NSF REU and a grant from the NU CS department, I was able to perform cutting-edge research on quantum computing.}%\normalsize
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Designed and programmed a quantum compiler to optimize quantum circuits for emerging quantum computer topologies.}

\resumeItem{Created a development framework and tools for further quantum systems research.}

\resumeItem{Student leader of the project while an undergraduate student.}

\resumeItemListEnd

\normalsize
\vspace{-4pt}


\resumeSubheading{Teaching Assistant}{%
  Jun 2023 -- Aug 2023\vspace{-2pt}%
}{%
  \href{https://www.mccormick.northwestern.edu/computer-science/academics/undergraduate/peer-mentor-program/}{Northwestern University}%
}{Evanston, IL}


\vspace{4pt}
\small{Acted as an undergraduate peer mentor for CS 321 Programming Languages.}%\normalsize
\vspace{-10pt}


\resumeItemListStart

\resumeItem{Held several office hours each week.}

\resumeItem{Answered questions, both synchronously in office hours and asynchronously on a Piazza message board.}

\resumeItemListEnd

\normalsize
\vspace{-4pt}


\resumeSubheading{Campus Ambassador}{%
  Sep 2023 -- Present\vspace{-2pt}%
}{%
  \href{https://ansys.com}{Ansys}%
}{Evanston, IL}



\resumeItemListStart

\resumeItem{Researched, reached out to, and scheduled meetings with relevant campus groups to discuss Ansys' tools.}

\resumeItem{Organized lunch info sessions for Ansys, including booking rooms and organizing food.}

\resumeItem{Coordinated with a member of the Ansys team for the campus work.}

\resumeItemListEnd

\normalsize
\vspace{-4pt}


\resumeSubHeadingListEnd
\vspace{-12pt}